What Can Stack Traces Tell us about the Use of Exceptions in Java?

### 2014-05-07 android-stacks.tex
Related work rework

In this section, we present works thaat are related to our own, distributed in
four categories: (i) works that use the information available on stack traces;
(ii) empirical studies on the usage of Java exceptions and its fault proneness;
(iii) tools to extract stack traces information from natural language artifacts
(i.e., issues and emails);  and (iv) empirical studies involving Android apps.

\textit{Analysis of Java Exception Usage.} Since the manual analysis of the Java
exception-flow can easily become infeasible Robillard and Murphy~\cite{Robil00}
developed a tool called Jex that analyzes the flow of exceptions in Java source
code. Based on java source code this tool performs dataflow analysis in order to
find the propagation paths of checked and unchecked exception types. After this
tool other tools have been proposed to support the static analysis of exception
flows ~\cite{fu2007exception} ~\cite{coelho2008assessing}. The main limitation
off all tools is the number of false positives inherent to static analysis
solutions, which can lead to a high number of exception flows, specially if
considering Java Environment exceptions and exceptions signaled from libraries.
This was the fist of some tools proposed to statically analyzed the exception
flow of exceptions. Cabral and Marques~\cite{cabral2007exception} analyzed the
exception handling code of 32 open-source systems, both for Java and .NET. The
goal of their study was to identify how exceptions were handled in different
categories of systems. They examined the exception handlers and the respective
actions taken on them. They observed that the action handlers were very simple
(e.g., logging and present a message to the user). In our work differs from
previous works since in our study we tried to identify bad practices from the
combined use of stack traces extracted from issues and bytecode and source code
analysis. Finally, Reimer and Srinivasan~\cite{reimer2003analyzing} listed a set
of bad practices on exception handling that hinder software maintainability and
robustness. Their differs from ours it was solely based on their own experience
on working with Java enterprise applications and focus on source code examples
of bad patterns on ways of handling exceptions such as exception swallowing, log
verbosity.

\textit{Analysis and Use of Stack Trace Information.} Some works have
investigated the usage of stack trace information to support bug classification
and clustering~\cite{wang2013improving, kim2011crash, dhaliwal2011classifying},
fault-proneness prediction models~\cite{kim2013predicting} and even automated
bug fixing~\cite{sinha2009fault} tools.Kim et al~\cite{kim2011crash} use of
crash graphs (an aggregated form of multiple stack traces available in crash
reports) to detect duplicate crash reports and to predict if a given crash will
be fixed. Dhaliwal et al~\cite{} analyzed crash reports collected for Mozilla
Firefox and proposed a crash grouping approach based on the Levenshtein
distance. This work showed that a crash grouping approach can reduce bug fixing
time in approximately 5\%. Wang et al~\cite{} proposes an approach to define
correlated crash types automatically. Moreover it also provides a bug
localization method to locate and rank files related to the bug described on a
stack trace.  Schroter et al~\cite{schroter2010stack} conducted an empirical
study on the usefulness of stack traces for bug fixing. The study used the
development data of Eclipse project and could observe that developers fixed the
bugs faster when failing stack traces were included on bug issues. This study is
aligned with the one performed by Bettenburg et al. ~\cite{bettenburg2008makes}
which evaluated what content could make a good bug report, and stack traces were
mentioned as the second most important content for developers - just after the
"steps to reproduce" information. Sinha et al~\cite{sinha2009fault} proposed an
approach for locating and repairing faults that are caused by JVM implicitly
signaled exceptions related to coding errors such as NullPointerExceptions. This
approach uses the information available on the stack trace to guide a dataflow
analysis, to locate the source statement responsible for the exception. Kim at
al.~\cite{kim2013predicting} proposed an approach to predict the crash-proneness
of methods based information extracted from stack traces and methods' bytecode
operations. They used InfoZilla to extracted stack trace information from the
bug reports of two open-source projects, i.e. AspectJ and Eclipse. They could
observe that most of the stack traces were related to NullPointerException and
other JMV implicitly thrown exceptions had the higher prevalence on the analyzed
set of stacks.

\textit{Extracting Stack Traces from Natural language artifacts.} Nowadays many
software vendors embed automatic crash reporting tools in their software
systems. Hence, whenever a software crashes this tool sends a detailed crash
report to its vendors. Moreover, there are also find third party software
solutions specialized in bug reporting, most of them for the increasing marked
of mobile apps~\cite{BugSe14,BugSn14,Googl14,Acra14}. Hence most of the works
described previously used the  information provided by crass reporting tools.
Two works have proposed tools extract stack traces from natural language
artifacts such as issues and emails: Infozilla ~\cite{bettenburg2008extracting}
is based on a set of regular expressions that extract an the set of frames
related to a stack trace, the main limitation of this solution is that it is not
able to extract stack traces embedded on verbose log files (i.e., on which we
can find log text mixed with exception frames). Alberto and Lanza
~\cite{bacchelli2012content}  propose a solution to recognize stack trace frames
from development emails and relate it to code artifacts (i.e. classes) mentioned
on the stack trace.

\textit{Empirical studies using Android apps.} Ruiz et al.~\cite{Ruiz12}
investigated the degree of reuse across applications in Android Market, the
study showed that almost 23\% of the classes inherited from a base class in the
Android API, and that 217 mobile apps were reused completely by another mobile
app. Pathak et al.~\cite{Patha11} analyzed bug reports and developers
discussions of Android platform and found out that approximately 20\% of
energy-related bugs in Android occurred after an OS update. McDonnell et
al.~\cite{McDon13} conducted a case study of the co-evolution behavior of
Android API and 10 dependent applications using the version history data found
in github. The study found that approximately 25\% of all methods in the client
code used the Android API, and that the methods reusing fast-evolving APIs were
more defect prone then others. Vásquez et al.~\cite{Linar13} analyzed
approximately 7K free Android apps and observed that the last successful apps
used Android APIs that were on average 300\% more change-prone than the APIs
used by the most successful apps. Pingyu and Elbaum~\cite{Zhang12} analyzed bug
reports of 5 Android applications an observed that 29\% had to do with poor
exceptional handling code.  Our work differs from the others as it aims at
distilling the information of bug reports describing uncaught exceptions created
for mobile applications in Github and Googlecode, in order to get a first view
of what is causing the crashes across applications available and what the
characteristics of the stack traces can tell us about the exception structure of
those applications. %Moreover this work\ldots.

>>>>

In this section, we present works that are related to our own, distributed in
four categories: i) works that use the information available on stack traces;
ii) empirical studies on the usage of Java exceptions and its fault proneness;
iii) tools to extract stack traces information from natural language artifacts
(i.e., issues and emails), and iv) empirical studies involving Android apps.

\textit{Analysis of Java Exception Usage.} Since the manual analysis of the Java
exception flow can easily become infeasible, Robillard and Murphy~\cite{Robil00}
employed dataflow analysis to find the propagation paths of checked and
unchecked exception types. Modeled after Robillard and Murphy's work, other
tools have been proposed to support the static analysis of exception
flows~\cite{coelho2008assessing}. The main limitation off all
static analysis tools is the number of false positives inherent to static analysis
solutions, which can lead to a high number of exception flows, specially if
considering Java Environment exceptions and exceptions signaled from libraries.

Additionally, Cabral and Marques~\cite{cabral2007exception} analyzed the
exception handling code of 32 open-source systems, both for Java and .NET. They
observed that the action handlers were very simple (e.g., logging and present a
message to the user). Reimer and Srinivasan~\cite{reimer2003analyzing} listed a
set of bad practices on exception handling that hinder software maintainability
and robustness, based on their own experience with Java enterprise applications.
Our work differs from those two works as we tried to identify bad practices from
the combined use of stack traces extracted from issues and bytecode and source
code analysis.

\textit{Analysis and Use of Stack Trace Information.} Several works have
investigated the use of stack trace information to support bug classification
and clustering~\cite{wang2013improving, kim2011crash, dhaliwal2011classifying},
fault-proneness prediction models~\cite{kim2013predicting} and even automated
bug fixing tools~\cite{sinha2009fault}. Kim et al.~\cite{kim2011crash} use an
aggregated form of multiple stack traces available in crash reports to detect
duplicate crash reports and to predict if a given crash will be fixed. Dhaliwal
et al.~\cite{dhaliwal2011classifying} proposed a crash grouping approach that
can reduce bug fixing time in approximately 5\%. Wang et
al.~\cite{wang2013improving} propose an approach to identify correlated crash
types and describe a fault localization method to locate and rank files related
to the bug described on a stack trace. Schroter et al.~\cite{schroter2010stack}
conducted an empirical study on the usefulness of stack traces for bug fixing
and showed that developers fixed the bugs faster when failing stack traces were
included on bug issues.  In a similar study, Bettenburg et
al.~\cite{bettenburg2008makes} identify stack traces as the second most stack
trace feature for developers.  Sinha et al.~\cite{sinha2009fault} proposed an
approach that uses stack traces to guide a dataflow analysis for locating and
repairing faults that are caused by the JVM implicitly signaled exceptions. Kim
at al.~\cite{kim2013predicting} proposed an approach to predict the
crash-proneness of methods based information extracted from stack traces and
methods' bytecode operations.  They observed that most of the stack traces were
related to NullPointerException and other JMV implicitly thrown exceptions had
the higher prevalence on the analyzed set of stacks.

\textit{Extracting Stack Traces from natural language artifacts.} 
%Currently, many
%software vendors embed automatic crash reporting tools in their software
%systems. Moreover, third party crash collection services exist, most of them 
%targeted for applications run on mobile phones~\cite{BugSe14,BugSn14,Googl14,Acra14}.
Apart from bug reports, stack traces can be embedded in other forms of
communication between developers, such as discussion logs and emails.
Being intermixed with text makes the accurate extraction of stacktraces 
an involved process.
Infozilla~\cite{bettenburg2008extracting}
is based on a set of regular expressions that extract a set of frames
related to a stack trace. The main limitation of this solution is that it is not
able to extract stack traces embedded on verbose log files (i.e., on which we
can find log text mixed with exception frames). Bacchelli and Lanza
~\cite{bacchelli2012content} propose a solution to recognize stack trace frames
from development emails and relate it to code artifacts (i.e. classes) mentioned
on the stack trace. In addition to those tools, ExceptionMiner is able to 
both extract stack traces from natural language artifacts and to 
classify them in a set of predefined categories.

\textit{Empirical studies using Android apps.} Ruiz et al.~\cite{Ruiz12}
investigated the degree of reuse across applications in Android Market, the
study showed that almost 23\% of the classes inherited from a base class in the
Android API, and that 217 mobile apps were reused completely by another mobile
app. Pathak et al.~\cite{Patha11} analyzed bug reports and developers
discussions of Android platform and found out that approximately 20\% of
energy-related bugs in Android occurred after an OS update. McDonnell et
al.~\cite{McDon13} conducted a case study of the co-evolution behavior of
Android API and 10 dependent applications using the version history data found
in github. The study found that approximately 25\% of all methods in the client
code used the Android API, and that the methods reusing fast-evolving APIs were
more defect prone then others. Vásquez et al.~\cite{Linar13} analyzed
approximately 7K free Android apps and observed that the last successful apps
used Android APIs that were on average 300\% more change-prone than the APIs
used by the most successful apps. Pingyu and Elbaum~\cite{Zhang12} analyzed bug
reports of 5 Android applications an observed that 29\% had to do with poor
exceptional handling code. Our work differs from the others as it aims at
distilling the information of bug reports describing uncaught exceptions created
for mobile applications in Github, in order to get a first view
of what is causing the crashes across applications available and what the
characteristics of the stack traces can tell us about the exception structure of
those applications.
